Graph Topology Learning from Binary Signals on Graph

### 2022-04-26 poster html copy/poster html.Rmd
Updated final draft of poster.

Consider the proabability mass function for a given $A$ and signal $y = Y[,k]$
\begin{align}
P_{Ah}(y_i) &= p^{y_i}(1-p)^{1-y_i} \\
            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(1- \frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{1-y_i} \\
            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(\frac{1}{1 + e^{A[i,]h}}\right)^{1-y_i}   \\
            &= \frac{e^{y_iA[i,]h}}{1 + e^{A[i,]h}}

@@

Ground Truth               |  Estimation 
:-------------------------:|:-------------------------:
![](pictures/gt_A_heatmap.png){width=125%}  |  ![](pictures/est_A_heatmap.png){width=125%}

>>>>

Consider the probability mass function for a given $A$ and signal $y = Y[,k]$
\begin{align}
P_{Ah}(y_i) &= p^{y_i}(1-p)^{1-y_i} \\
            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(1- \frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{1-y_i} \\
            &= \left(\frac{e^{A[i,]h}}{1 + e^{A[i,]h}}\right)^{y_i}\left(\frac{1}{1 + e^{A[i,]h}}\right)^{1-y_i}   \\
            &= \frac{e^{y_iA[i,]h}}{1 + e^{A[i,]h}}

@@

##### Synthetic Data Generation

To generate a single signal for a given adjacency matrix $A \in \mathbb{R}^{N\times N}$ and latent factor vector $h \in \mathbb{R}^N$ (each $h_i \sim \mathcal{N}(0,1)$), a vector of odds, $Ah$, is compared to a vector $T$, where $T_i$ selected uniformly at random for each $i = 1, \ldots , N$. If $T_k < Ah_k$, then node $k$ takes the signal value of $1$, and $0$ otherwise. We generate $M = 100$ synthetic signals, and use them to learn an adjacency matrix. The learned graph is found with parameter values $\alpha = .2$, $a = 1$ and $b = -1$.

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Ground Truth** &nbsp; &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**Learned**

![](pictures/gt_A_heatmap.png){width=45%}  ![](pictures/est_A_heatmap.png){width=45%}
